\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{4.08003pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingg}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjSubheadingg}[2]{
  \vspace{-2pt}
  
    % \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
    \begin{itemize}
       \item {#1}   \hspace*{\fill}{\textbf{\small #2}} 
    \end{itemize}
    \vspace{-12pt}
    
    % \end{tabular*}
    
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    {\Huge \scshape Harsh Gupta} \\ \vspace{8pt}
    
    \small 
    \href{mailto:hg242322@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{hg242322@gmail.com}} ~ 
    \href{tel://+917001876232}{\raisebox{-0.2\height}\faPhone\   \underline{+91 7001876232}} ~
    \href{https://www.linkedin.com/in/harsh-gupta-707a331b4/}{\raisebox{-0.2\height}\faLinkedin\ \underline{harsh-gupta-707a331b4}}  ~
    \href{https://github.com/guptaharsh13}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/guptaharsh13}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vellore Institute of Technology, Vellore}{Jul 2020 -- May 2024 (Expected)}
      {B.Tech in Computer Science and Engineering}{9.10, CGPA}

      % \resumeSubheading
      % {St. Patrick's Higher Secondary School, Asansol}{Apr 2018 -- Apr 2020}
      % {Indian School Certificate (ISC)}{95\%}

      % \resumeSubheading
      % {St. Patrick's Higher Secondary School, Asansol}{Apr 2012 -- Apr 2018}
      % {Indian Certificate of Secondary Education (ICSE)}{96.4\%}
  \resumeSubHeadingListEnd
  \vspace{-12pt}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheadingg
      {\href{https://www.luganodes.com/}{Luganodes} (Software Development Engineer)}{Sep 2023 -- Present}
      \resumeItemListStart
        \resumeItem{Developed robust indexers for Ethereum, \href{https://github.com/Luganodes/Solana-Indexer}{Solana (open-sourced)}, Polkadot, Polygon, MultiversX, and Kava, ensuring efficient and accurate data indexing.}
        \resumeItem{Developed a custom deposit tracker for our Ethereum staking API, with over \$1 billion in client stakes, eliminating reliance on Beaconcha.}
        \resumeItem{Engineered a sophisticated reporting dashboard, with end-to-end deployment (inc. CI/CD integration), providing accurate financial reports for clients with over \$2.5 billion in stakes.}
        \resumeItem{Automated monthly asset reports across 20 blockchains, improving efficiency and report reliability.}
    \resumeItemListEnd
    % \vspace{-6pt}

\resumeSubheadingg
      {\href{https://dyte.io/}{Dyte} (Software Engineering Intern)}{May 2023 -- Aug 2023}
      \resumeItemListStart
        \resumeItem{Conducted load testing on socket services, achieving 100K simultaneous socket connections to verify its reliability and robustness.}
        \resumeItem{Developed unit tests for 2 major socket services in Go, with a 90\% test coverage, automating the report generation using a CI/CD pipeline.}
        \resumeItem{Developed a health probe to monitor the status of socket services and generate automated reports sent to Slack.}
    \resumeItemListEnd
    % \vspace{-6pt}
    
  \resumeSubHeadingListEnd

\vspace{-12pt}

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

  \resumeSubheadingg
      {\href{https://github.com/guptaharsh13/rbac-auth-service/}{RBAC Authentication Service}}{}
      \resumeItemListStart
        \resumeItem{Developed an extensive, containerized task management system featuring customizable, dynamic role-based access control (RBAC).}
        \resumeItem{Ensured robust security with advanced user authentication, data integrity, and privacy measures.}
    \resumeItemListEnd
    % \vspace{-6pt}

 \resumeSubheadingg
      {{Email Extractor}}{}
      \resumeItemListStart
        \resumeItem{Automated IEEE VIT's sponsorship workflow using Selenium WebDriver and Python3, achieving a 300\% increase in sponsorship revenue compared to the previous year}
        \resumeItem{Managed a high-volume email system, integrating AWS SES, SendGrid, and Mailgun to efficiently send over 10,000 emails per event for organization events.}
    \resumeItemListEnd
    \vspace{-6pt}

    
    \resumeSubheadingg
      {\href{https://github.com/guptaharsh13/circulo}{Círculo}}{}
      \resumeItemListStart
        \resumeItem{Built an API for retrieving recent YouTube videos by tag/search query, in a paginated response}
        \resumeItem{Innovated an optimized algorithm based on exponential backoff, dynamically adjusting request intervals using Celery and Celery Beat.}
        \resumeItem{Enhanced database performance with BRIN indexing, and partially implemented Elasticsearch for advanced search.}
        
    \resumeItemListEnd
    \vspace{-6pt}

    \resumeSubheadingg
      {\href{https://github.com/guptaharsh13/FFCS}{FFCS}}{}
      \resumeItemListStart
        \resumeItem{Developed a TypeScript backend for a University Credit and Timetable Management System, enhancing efficiency and preventing scheduling conflicts.}
        \resumeItem{Utilized PostgreSQL for reliable data management, adhering to OpenAPI standards for API integration.}

    \resumeItemListEnd
    % \vspace{-6pt}
    
  \resumeSubHeadingListEnd
\vspace{-12pt}

%-----------LEADERSHIP---------------
\section{Leadership / Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheadingg{{Technical Lead, \href{https://ieeevit.org}{IEEE-VIT}}}{Dec 2020 -- Dec 2023}
            \resumeItemListStart
                \resumeItem{Responsible for Technical growth of 75+ members in the organization inculcating and promoting the Open Source Software culture and good development practices.}
                \resumeItem{Developed software for events and projects used by 1500+ participants in 100+ countries.}
                \resumeItem{Speaker at “\href{https://youtu.be/qxFbK-CRbO8}{Techloop -- Introduction to MERN}”, guiding 400+ students in Web Development.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
    

\vspace{-12pt}

% -----------Achievements-----------
\section{Achievements}
    \resumeItemListStart
       \resumeItem{Awarded the Merit Scholarship for Outstanding Performance in academics by VIT Vellore, twice.}
       \vspace{-6pt}
   \resumeItemListEnd
   
% -----------SKILLS AND INTERESTS--------
\section{Skills and Interests}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Programming Languages}{: Go, JavaScript, TypeScript, NodeJS, Python3, Java, C, C++}
        \textbf{Relevant Coursework}{:  Data Structures and Algorithms, Database Management Systems, Objected Oriented Programming, Operating Systems, Computer Networks, Computer Architecture and Organization, Theory of Computation, Cryptography Fundamentals, Cyber Security, Network Security, Web Security}
        \textbf{Miscellaneous}{:  Linux, Git, GitHub, Jira, Postman, PostgreSQL, MongoDB, MySQL, Azure, AWS, GCP}
        \textbf{Qualities}{: Confident, Multitasker, Quick-learner, Adaptive, Team player, Problem Solving}
    }}
 \end{itemize}
 
\vspace{-12pt}

\end{document}
